A Low-cost Natural Interaction System based on a Camera Hand-Gestures Recognizer

### 2011-02-04 paper.tex
add CCL + some refs

We present in this paper an approach that could allow the detection and the
interpretation of gestures of a TV spectator from a simple and low cost camera. 
RevTV is the name of the French project for adding new interaction techniques
to TVs to allow the inclusion of the telespectator.
%Pourquoi as-tu enlevé cette phrase (ligne suivante) ? Cela me semblait une bonne introduction à la présentation du projet.

%The final objective of this study is to control the animations of an avatar that should be inserted within a TV show beside the presenter or actor [RevTV].
One major scenario that we rely on, corresponds to some educational game where a pupil
controls his/her avatar which interact in a forecast program led by a ``real'' TV animator.
During such kind of scenarios, commands interaction
like pointing, selecting and moving, as well as natural gesture animation, are required.

\ignore{
%The final objective of this study is to control the animations of an avatar
%that should be inserted within a TV show beside the presenter or actor [RevTV].
Its major scenario which we rely on, corresponds to educational games where a
pupil controls his/her avatar in a program led by a ``real'' TV animator.
This kind of scenarios needs to be able to manage commands interaction
like pointing, selecting and moving as well as natural gesture animation.
}
% Il faut rajouter une description du projet Rev-TV

\section{Gesture Semantics}
Gestures do not come alone, they are combined with speech, or with cognitive
activity. We study in this part the sources of gestures and the relation between
them and other activities.
First sources of gestures can come from the interaction between two human in a
discussion, these type of gestures are used to add more precision on the details
and they are made by the same auditory areas of the cortex \cite{SymbolicGest}.

@@

\subsection{Gestures taxonomies}
A rapid look the possible gestures human can perform \cite{Gesturecraft},
lead to the conclusion that the amount of possibilities is tremendous.
Nonetheless, the gestures can be classified according to various criteria not
only to simplify their recognition, but also to allow their reproducing on an
avatar to putting tags on them for future analysis\cite{gestureRecreation}.
Here, we consider a taxonomy based on the context of the gestures as well as on their types:
%%%%%%%
%By looking at the possible gestures human can generate \cite{Gesturecraft}, we
%get a huge amount of possibilities which depend on the context and on the type.

%So, there is a need for a taxonomy.
%Many possible taxonomies exist according to the technical or analytical aspects:
%In order to describe and analyse each gesture, we can rely on the following aspects:
\ignore{\begin{description}
 \item[Gesture Creation Space:] We use this criteria to distinguish between gestures made in the 2D or 3D space.
 \item[Number of used strokes:] We use this criteria to distinguish between gestures constructed by only one path and between those using many paths, so the recognition needs to wait for all strokes before the recognition
 \item[Gesture context:] We use this criteria to distinguish gesture based on the specific use of it, gestures for disabled people, gestures in talk-shows, gestures in meetings.
\end{description}}
%Gesture and Thoughts, page 18
According to McNail \cite{gestureThought}, it is possible and useful to
distinguish between these gestures and a possible taxonomy can provide us these
types:
\begin{description}
 \item[Gesticulation] is a motion that embodies a meaning reliable to the
accompanying speech. It is made chiefly with the arms and hands but is not
restricted to these body parts.
 \item[Speech-linked gestures] are parts of sentences themselves, the gesture
completes the sentence structure.
 \item[Emblems] are conventionalized signs, such as thumbs-up or the ring (first
finger and thumb tips touching, other fingers extended) for ``OK.''
 \item[Pantomime] is dumb show, a gesture or sequence of gestures conveying a
narrative line, with a story to tell, produced without speech.
\end{description}

@@

%Fig. Skin segmentation
% Testing graphics
\png{skincolor}{Skin color}
\section{Blobs Tracking}
After having the hands and head blobs identified, an efficient
tracking method based on the apparence model for occlusion handling\cite{app06}.
We have used the cvblob implementation \cite{cvblob} for that algorithm which 
stores the mesures of bounding boxes distance and provide tracks instead of just blobs.  %distantBlobTrack.

@@

\section{System integration of this interaction and future work}

Our system support gestural interaction at the moment but the integration of
other multimodal ways are possible to fine tune the input and give the user
feedback.
These possible evolution of the system are possible:

@@

\ignore{
Gesture + facial recog.
Voice recognition
Haptic 
--
Naturalness came from the analysis of gestures used in talk shows.
(gestures used many times means nature gestures)
Reverse thinking.
Usability in the context of RevTV ??
}
% ---- Bibliography ----
\bibliographystyle{splncs03}
\bibliography{paper}

>>>>

We present in this paper an approach that could allow the detection and the
interpretation of gestures of a TV spectator from a simple and low cost camera. 
RevTV is the name of the French project for adding new interaction techniques
to TVs to allow the inclusion of the telespectator.

The final objective of this study is to control the animations of an avatar
that should be inserted within a TV show beside the presenter or actor.
One major scenario that we rely on, corresponds to some educational game where a pupil
controls his/her avatar which interact in a forecast program led by a ``real'' TV animator.
During such kind of scenarios, commands interaction
like pointing, selecting and moving, as well as natural gesture animation, are required.

% Il faut rajouter une description du projet Rev-TV
%Le dernier paragraphe n'est pas une description ?

\section{Gesture Semantics}
Symbolic gestures, such as emblems, play an important role in human
communication as they can fully take the place of words.
These gestures and spoken language are processed by the same system in the human brain.

Results support a model in which bilateral modality-specific areas in superior and inferior temporal cortices extract salient features from vocal-auditory and gestural-visual stimuli respectively.
However, both classes of stimuli activate a common, left-lateralized network of inferior frontal and posterior temporal regions in which symbolic gestures and spoken words may be mapped onto common, corresponding conceptual representations.

Gestures do not come alone, they are combined with speech, or with cognitive
activity. We study in this part the sources of gestures and the relation between
them and other activities.
First sources of gestures can come from the interaction between two human in a
discussion, these type of gestures are used to add more precision on the details
and they are made by the same auditory areas of the cortex \cite{SymbolicGest}.

@@

\subsection{Gestures taxonomies}
A rapid look the possible gestures human can perform \cite{Gesturecraft},
lead to the conclusion that the amount of possibilities is tremendous.
Nonetheless, the gestures can be classified according to various criteria not
only to simplify their recognition, but also to allow their reproducing on an
avatar to putting tags on them for future analysis\cite{gestureRecreation}.
Here, we consider a taxonomy based on the context of the gestures as well as on their types:
%%%%%%%
%By looking at the possible gestures human can generate \cite{Gesturecraft}, we
%get a huge amount of possibilities which depend on the context and on the type.
%So, there is a need for a taxonomy.
%Many possible taxonomies exist according to the technical or analytical aspects:
%In order to describe and analyse each gesture, we can rely on the following aspects:
\ignore{\begin{description}
 \item[Gesture Creation Space:] We use this criteria to distinguish between gestures made in the 2D or 3D space.
 \item[Number of used strokes:] We use this criteria to distinguish between gestures constructed by only one path and between those using many paths, so the recognition needs to wait for all strokes before the recognition
 \item[Gesture context:] We use this criteria to distinguish gesture based on the specific use of it, gestures for disabled people, gestures in talk-shows, gestures in meetings.
\end{description}}
%Gesture and Thoughts, page 18
According to McNail \cite{gestureThought}, it is possible and useful to
distinguish between these gestures and a possible taxonomy can provide us these
types:
\begin{description}
 \item[Gesticulation] is a motion that embodies a meaning reliable to the
accompanying speech. It is made chiefly with the arms and hands but is not
restricted to these body parts.
 \item[Speech-linked gestures] are parts of sentences themselves, the gesture
completes the sentence structure.
 \item[Emblems] are conventionalized signs, such as thumbs-up or the ring (first
finger and thumb tips touching, other fingers extended) for ``OK.''
 \item[Pantomime] is dumb show, a gesture or sequence of gestures conveying a
narrative line, with a story to tell, produced without speech.
\end{description}

@@

\png{skincolor}{Skin color}

\section{Blobs Tracking}
After having the hands and head blobs identified, an efficient
tracking method based on the appearance model for occlusion handling\cite{app06}.
We have used the cvblob implementation \cite{cvblob} for that algorithm which 
stores the measures of bounding boxes distance and provide tracks instead of just blobs.  %distantBlobTrack.

@@

\section{System integration of this interaction and future work}
Human brain perisylvian areas, identified as the core of the brain's language
system, are not in fact committed to language processing, but may function as a
modality-independent semiotic system that plays a broader role in human
communication, linking meaning with symbols whether these are words, gestures,
images, sounds, or objects \cite{SymbolicGest}.
This natural handling of multimodal communications gives an argument to build
recognizer taking part of most of these modalities specially to remove ambiguous
gesture meaning decision cases.

Our system only supports gestural interaction at the moment but the integration
of other multimodal means are possible to fine tune the input and give the user
better feedback.
These possible evolution of the system are possible:

@@

\section*{Conclusion}
In this paper we have shown a proof-of-concept mechanism to recognize hand
gestures then use them to control a TV or to take actions in a Game scenario.
We have also freely provided a library which can be used to represent gestures
in other scenarios.
The evolution of our system is being discussed to add more modalities even if we
are aware of some of the limits \cite{Oviatt99tenmyths}.

% ---- Bibliography ----
\bibliographystyle{splncs03}
\bibliography{paper}
